Computing Entropies With Nested Sampling

### 2017-07-11 paper/ms.tex
Editing the conclusion

Throughout this paper, the question of how to sample from the constrained
distributions required by NS has not been discussed in detail. For the examples,
I used the original \citet{skilling2006nested} suggestion of using a short MCMC run
initialised at a surviving point. In some problems, this will not be effective,
and this will cause the resulting estimates to be incorrect, as in standard
Nested Sampling applications. Despite this, the algorithm should be
useful in a wide range of applications.

>>>>

Throughout this paper, the question of how to sample from the constrained
distributions required by NS has not been discussed in detail. For the examples,
I used the original \citet{skilling2006nested} suggestion of using a short MCMC run
initialised at a surviving point. In some problems, this will not be effective,
and this will cause the resulting estimates to be incorrect, as in standard
Nested Sampling applications. Testing the sensitivity of the results to
changes in the number of MCMC steps used is a simple way to increase one's
confidence in the results, but is not a guarantee.
Despite this weakness, I hope the algorithm will be
useful in a wide range of applications.
